Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-01-14 latex/comp_or.tex
New parallel pallets shims working fine.
Started parallel greedy
New shims still not working
Trying without queue, with lock
New tests accomplished but Shims_mp still does not work within the main file
Testing Gurobi
Check Gurobi results on testing

%\usepackage{hyphenat}
\usepackage[none]{hyphenat}

@@

Transport aviation faces risks of cargo imbalance in the set of circumstances of aerial pickup and shipment of goods in a distribution system given the urgency required for loading for fast takeoff and mission accomplishment, notably in moments of crisis, public emergency, client contract short turnaround times, or any external forces for instant takeoff. Additionally, there is no computer support to aid load and trip programmers with the massive transportation demands in each location.

@@

\begin{table}[H]
	\centering
	\caption{Volume surpluses, methods and scenarios results}  \label{tab:results}
	\footnotesize
	%\scriptsize
	\begin{tabular}{cccccccccc}
		\toprule
		              &            &                  &\multicolumn{6}{c}{\bf Scenarios}              &{\bf Normalized}\\
		\cmidrule{4-9}		
		{\bf Surplus} & {$method$} &{\bf Results}     &{\bf 1}&{\bf 2}&{\bf 3}&{\bf 4}&{\bf 5}&{\bf 6}&{\bf Speed-up} \\
		\toprule

		\multirow{8}{*}{$1.2$} &\multirow{2}{*}{ $mpShims^{0.7s}$}& $f$               &   &   &   &   &   &   &   \\%
                               &                                 & {\bf run-time (s)} &      &      &      &     &     &    &   \\%\cmidrule{2-10}

		                       &\multirow{2}{*}{ $mpShims^{0.7s}$}& $f$               & 5.70  & 3.09  & 2.94  & 2.90  & 2.79  & 5.70  & 0.91  \\%2312
		                       &                                 & {\bf run-time (s)} & 1     & 3     & 7     & 26    & 97    & 267   & 70  \\%390
		                       \cmidrule{2-10}
		                       &\multirow{2}{*}{ $mpACO^{60s}$}   & $f$               & 6.42  & 3.78  &  3.19 & 3.17  & 2.97  & 5.87  & 1.00  \\ %2540
                               &                                 & {\bf run-time (s)} & 16    & 282   &  314  & 1334  & 6945  & 18883 & 1  \\ %27162
		\cmidrule{2-10}		                       
							   &\multirow{2}{*}{ $mpACO^{0.7s}$}  & $f$               &&&&&&&\\
							   &                                 & {\bf run-time (s)} &&&&&&&\\                               
		\midrule
		\multirow{6}{*}{$1.5$} &\multirow{2}{*}{ $mpShims^{0.7s}$}& $f$               & 8.15  & 4.22  & 4.40  & 4.01  & 3.51  & 7.08  & 0.91  \\%3137
		                       &                                 & {\bf run-time (s)} & 1     & 5     & 12    & 45    & 244   & 737   & 30  \\%1026
		\cmidrule{2-10}
		                       &\multirow{2}{*}{ $mpACO^{60s}$}   & $f$               & 9.50  & 5.01  & 4.60  & 4.28  & 3.78  & 7.15  & 1.00 \\ %3432

		                       &                                 & {\bf run-time (s)} & 9     & 344   & 787   & 1525  & 7525  & 21443 & 1 \\%30493
		\cmidrule{2-10}		                       
							   &\multirow{2}{*}{ $mpACO^{0.7s}$}  & $f$               &&&&&&&\\
							   &                                 & {\bf run-time (s)} &&&&&&&\\		                       
		\midrule
		\multirow{6}{*}{$2.0$} &\multirow{2}{*}{ $mpShims^{0.7s}$}& $f$               & 11.31 & 6.29  & 5.54  & 5.83  & 5.05  & 10.63 & 0.94  \\%4465
		                       &                                 & {\bf run-time (s)} & 2     & 14    & 34    & 106   & 477   & 2417  & 10  \\%3000
		\cmidrule{2-10}
		                       &\multirow{2}{*}{ $mpACO^{60s}$}   & $f$               & 12.70 & 7.09  & 5.97  & 5.91  & 5.31  & 10.69 & 1.00  \\%4767
		                       &                                 & {\bf run-time (s)} & 5     & 189   & 784   & 1456  & 7758  & 20330 & 1  \\%29544
		\cmidrule{2-10}		                       
		                       &\multirow{2}{*}{ $mpACO^{0.7s}$}  & $f$                &&&&&&&\\
							   &                                 & {\bf run-time (s)} &&&&&&&\\
		\bottomrule

	\end{tabular}
\textsuperscript{The numbers 0.7s and 60s as superscript on the methods names represent the time limit per node.}	
\normalsize
\end{table}

>>>>

\usepackage[none]{hyphenat}

@@

Transport aviation faces risks of cargo imbalance in the set of circumstances of aerial pickup and shipment of goods in a distribution system given the urgency required for loading for fast takeoff and mission accomplishment, notably in moments of crisis, public emergency, client contract short turnaround times, or any external forces for instant takeoff. Furthermore, there is no computer support available to aid load and trip programmers with the massive transportation demands in each location.

@@

\begin{table}[H]
\centering
\caption{Volume surpluses, methods and scenarios results}  \label{tab:results}
\footnotesize
%\scriptsize
\begin{tabular}{crcccccccc}
\toprule
&                       &                           &\multicolumn{6}{c}{\bf Scenarios}              &{\bf Normalized}\\
\cmidrule{4-9}		
{\bf Surplus}           & {$method$}                &{\bf Results}       &{\bf 1}&{\bf 2}&{\bf 3}&{\bf 4}&{\bf 5}&{\bf 6}&{\bf Speed-up} \\
\toprule

\multirow{10}{*}{$1.2$} &\multirow{2}{*}{ $Shims$}  & $f$                &       &       &        &       &       &       &   \\%
&                                                   & {\bf run-time (s)} & < 1   &       &        &       &       &       &   \\%
\cmidrule{2-10}
&\multirow{2}{*}{ $mpShims$}                        & $f$                &       &       &        &       &       &       &   \\%
&                                                   & {\bf run-time (s)} & < 1   &       &        &       &       &       &   \\%

\cmidrule{2-10}
&\multirow{2}{*}{ $ACO$}                            & $f$                & 2.85  &       &        &       &       &       &   \\%
&                                                   & {\bf run-time (s)} & 15    &       &        &       &       &       &   \\%
\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpACO$}                          & $f$                & 3.63  &       &        &       &       &       &   \\%
&                                                   & {\bf run-time (s)} & 11    &       &        &       &       &       &   \\%

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Gurobi$}                         & $f$                & 6.35  &       &        &       &       &       &   \\%
&                                                   & {\bf run-time (s)} & 2     &       &        &       &       &       &   \\%

\midrule
\multirow{10}{*}{$1.5$} &\multirow{2}{*}{ $Shims$}  & $f$                &       &       &        &       &       &       &   \\%
&                                                   & {\bf run-time (s)} & < 1   &       &        &       &       &       &   \\%
\cmidrule{2-10}
&\multirow{2}{*}{ $mpShims$}                        & $f$                &       &       &        &       &       &       &   \\%
&                                                   & {\bf run-time (s)} & < 1   &       &        &       &       &       &   \\%

\cmidrule{2-10}
&\multirow{2}{*}{ $ACO$}                            & $f$                & 2.85  &       &        &       &       &       &   \\%
&                                                   & {\bf run-time (s)} & 15    &       &        &       &       &       &   \\%
\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpACO$}                          & $f$                & 3.63  &       &        &       &       &       &   \\%
&                                                   & {\bf run-time (s)} & 11    &       &        &       &       &       &   \\%

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Gurobi$}                         & $f$                & 6.35  &       &        &       &       &       &   \\%
&                                                   & {\bf run-time (s)} & 2     &       &        &       &       &       &   \\%

\midrule
\multirow{10}{*}{$2.0$} &\multirow{2}{*}{ $Shims$}  & $f$                &       &       &        &       &       &       &   \\%
&                                                   & {\bf run-time (s)} & < 1   &       &        &       &       &       &   \\%
\cmidrule{2-10}
&\multirow{2}{*}{ $mpShims$}                        & $f$                &       &       &        &       &       &       &   \\%
&                                                   & {\bf run-time (s)} & < 1   &       &        &       &       &       &   \\%

\cmidrule{2-10}
&\multirow{2}{*}{ $ACO$}                            & $f$                & 2.85  &       &        &       &       &       &   \\%
&                                                   & {\bf run-time (s)} & 15    &       &        &       &       &       &   \\%
\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpACO$}                          & $f$                & 3.63  &       &        &       &       &       &   \\%
&                                                   & {\bf run-time (s)} & 11    &       &        &       &       &       &   \\%

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Gurobi$}                         & $f$                & 6.35  &       &        &       &       &       &   \\%
&                                                   & {\bf run-time (s)} & 2     &       &        &       &       &       &   \\%

\bottomrule

\end{tabular}
%\textsuperscript{The numbers 0.7s and 60s as superscript on the methods names represent the time limit per node.}	
\normalsize
\end{table}
